### 2019-03-21 0_abstract.tex
Rewrite abstract.

\begin{abstract}
% 150 words
We introduce \emph{minimum effective task granularity} (METG), a new
metric for quantifying the fundamental performance behavior of
parallel and distributed runtime systems. METG is either directly
related to, or correlates with a variety of measures of direct
interest to application developers: namely the smallest problem size
that can be efficiently weak scaled, or the limit of strong
scalability. METG can be used to study the baseline overhead, scaling
behavior, and communication hiding ability of runtime systems, among
other properties.

We present Task Bench, a novel \emph{parameterized} benchmark for
exploring the behavior of parallel and distributed runtime
systems. Task Bench executes a configurable \emph{task graph} with
tasks for each point in an iteration space and dependencies determined
by a \emph{dependence relation}. We use Task Bench to conduct a
comprehensive evaluation of 13 runtime systems, and show that the
baseline overhead of these systems varies by up to 5 orders of
magnitude.
\end{abstract}

>>>>

\begin{abstract}
% 153 words
We present Task Bench, a \emph{parameterized} benchmark designed to
explore the performance envelops of parallel and distributed
programming systems under a variety of application scenarios. Task
Bench consists of a configurable \emph{task graph} with one task per
point in an iteration space, and dependencies between tasks determined
by a dependence relation. Tasks can execute a variety of kernels,
including compute- and memory-bound, and task dependencies carry
payloads of configurable size, enabling communication-bound use
cases. Multiple task graphs can be executed to enable task
parallelism.

We conduct a comprehensive comparative study with implementations of
Task Bench in 13 programming systems on up to 256 Haswell nodes of the
Cori supercomputer. We use a novel metric, \emph{minimum effective
  task granularity} to study the baseline runtime overhead of each
system and the impact of varying dependence patterns and number of
dependencies. We also study each system's scalability, and ability to
hide communication and mitigate load imbalance.
\end{abstract}
